Setup

### 2019-09-26 analysis/setup.Rmd
Update due to merge of PR in rticles

* `rticles`: from [`rstudio`](https://github.com/rstudio/rticles) if
  [PR #247](https://github.com/rstudio/rticles/pull/247) has been merged
  ```{r, eval=FALSE}
  install.packages("rticles")
  ```
  otherwise directly from [PR #247](https://github.com/rstudio/rticles/pull/247)
  ```{r, eval=FALSE}
  remotes::install_github("rstudio/rticles#247")
  ```

>>>>

* `rticles`: from [`rstudio`](https://github.com/rstudio/rticles) if
  [PR #247](https://github.com/rstudio/rticles/pull/247) has been merged and released on CRAN
  ```{r, eval=FALSE}
  install.packages("rticles")
  ```
  otherwise directly from [Github](https://github.com/rstudio/rticles/)
  ```{r, eval=FALSE}
  remotes::install_github("rstudio/rticles")
  ```
